PLAE enables quick and easy searching across one million ocular transcriptomes

### 2022-07-17 manuscript_00.Rmd
jpdates

```{r Setup..., message=FALSE, warning=FALSE, include=FALSE}
#knitr::opts_chunk$set(fig.pos = 'p') # Places figures on their own pages
knitr::opts_chunk$set(out.width = '100%', dpi=300)
library(tidyverse)
library(citr)
library(cowplot)
library(ggrepel)
library(colorspace)
library(flextable)
library(captioner)
library(glue)
library(tictoc)
#tic()()
#data_dir_vGiga <- '/Volumes/McGaughey_S/data/scEiaD/'
#data_dir_vPLAE <- '/Volumes/McGaughey_S/data/scEiaD_2022_02/'
data_dir_vGiga <- '~/data/scEiaD_gigascience/'
data_dir_vPLAE <- '~/data/scEiaD_2022_02/'
# setup caption-ing
fig_cap <- captioner("Figure")
supFig_cap <- captioner("Supplemental Figure")
tab_cap <- captioner("Table")
supTab_cap <- captioner("Supplemental Table")

@@

Cell type marker genes can be proposed on the basis of existing knowledge about their function and/or based on high expression differences when comparing to other cell types. We can further narrow down the list of markers by using the  diversity of studies and organisms in scEiaD to propose a set of community supported cell type markers. We first identify a set of well supported cell types which we define as cell types which have two or more independent studies across both human mouse (`r supTab_cap(name = 'well_supported_celltypes_tab', display = 'cite')`). These cell types were then assessed to identify differentially expressed genes which met the following criteria: 1. padj less than $1 x 10^-4$
in both human and mouse, 2. mean log2 fold change greater than two, and 3. mean padj less than $1 x 10^-5$

We filter down to only assess cell types with more than two independent datasets in both human and mouse. This leaves ..... These well supported cell types can be used to more strenuously identify genes that are consistently differentially expressed in a cell type across multiple species. To define these well supported marker genes we only ass

To identify genes that are differentially expressed across species we

>>>>

```{r Setup..., message=FALSE, warning=FALSE, include=FALSE}
#knitr::opts_chunk$set(fig.pos = 'p') # Places figures on their own pages
knitr::opts_chunk$set(out.width = '100%', dpi=300)
library(tidyverse)
library(citr)
library(cowplot)
library(ggrepel)
library(colorspace)
library(flextable)
library(captioner)
library(glue)
library(tictoc)
#tic()()
data_dir_vGiga <- '/Volumes/McGaughey_S/data/scEiaD/'
data_dir_vPLAE <- '/Volumes/McGaughey_S/data/scEiaD_2022_02/'
#data_dir_vGiga <- '~/data/scEiaD_gigascience/'
#data_dir_vPLAE <- '~/data/scEiaD_2022_02/'
# setup caption-ing
fig_cap <- captioner("Figure")
supFig_cap <- captioner("Supplemental Figure")
tab_cap <- captioner("Table")
supTab_cap <- captioner("Supplemental Table")

@@

Cell type marker genes can be proposed on the basis of existing knowledge about their function and/or based on high expression differences when comparing to other cell types. We can further narrow down the list of markers by using the  diversity of studies and organisms in scEiaD to propose a set of community supported cell type markers. We first identify a set of well supported cell types which we define as cell types which have two or more independent studies across both human and mouse (`r supTab_cap(name = 'well_supported_celltypes_tab', display = 'cite')`). These cell types were then assessed to identify differentially expressed genes which met the following criteria across human, mouse, and macaque: 1. padj less than $1 x 10^-4$
in two or more species, 2. mean log2 fold change greater than two, and 3. mean padj less than $1 x 10^-5$
